[\<- Back Home](index.html)

**Research Question:** What Oregon counties have the highest median income, but lowest high-school graduation rate?

Setup / Package loading

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Turn off scientific notation
options(scipen=999)

# Load the tidyverse.
library(tidyverse)
library(tidycensus)
library(leaflet.extras2)
library(glue)
library(mapview)
library(tmap)
```

Adding my API Key

```{r echo=FALSE}

myapikey <- "2a6f8c21a30d3024e038d67d7d4eba647dc79cd4"

census_api_key(myapikey, overwrite=TRUE, install = TRUE)

readRenviron("~/.Renviron")

```

Loading and setting variables

```{r}

Five_Year_ACS <- load_variables(2022, "acs5", cache = TRUE)

medincome <- "B19001_001E"
hsgrad <- "B15003_017E"
totalpop <- "B01003_001E"

myvars <- c(
  totalpop = "B01003_001E",
  medincome = "B19001_001E",
  hsgrad = "B15003_017E")
  
```

Creating tables and wrangling data

```{r}

MedianIncomeOregon <- 
  get_acs(geography = "county", 
          variables = medincome,
          state = "OR")
MedEdit <-
  rename(MedianIncomeOregon, income = estimate)
MedEdit <-
subset(MedEdit, select = -c(variable, moe) )

HighSchoolGradOregon <- 
  get_acs(geography = "county", 
          variables = hsgrad,
          state = "OR")
HSGradEdit <-
  rename(HighSchoolGradOregon, graduated = estimate)
```

Table if you'd like to see raw data without the map

```{r}
HSGradEdit <-
subset(HSGradEdit, select = -c(variable, moe) )
CombinedTable <-
  full_join(MedEdit, HSGradEdit)

```

Creating interactive map

```{r}
or_counties_withgeo <-
  get_acs(geography = "county",
          variables = c(myvars),
          state = "OR",
          output = "wide",
          geometry = TRUE)

map_income <- mapview(or_counties_withgeo, zcol = "medincome",col.regions  = RColorBrewer::brewer.pal(9, "Greens"),
        alpha.regions= 1)
map_hsgrad <- mapview(or_counties_withgeo, zcol = "hsgrad", col.regions  = RColorBrewer::brewer.pal(9, "Greens"),
        alpha.regions= 1)
map_totalpop <- mapview(or_counties_withgeo, zcol = "totalpop", col.regions  = RColorBrewer::brewer.pal(9, "Greens"),
        alpha.regions= 1)


```

Customizing labels and popups, adding percentage equation for HS Graduation Rate

```{r}
hsgrad_numeric <- as.numeric(or_counties_withgeo$hsgrad)
totalpop_numeric <- as.numeric(or_counties_withgeo$totalpop)

labels <- glue::glue("{or_counties_withgeo$NAM} Median Income of {or_counties_withgeo$medincome}, High School Graduation Rate of {(100-((hsgrad_numeric/totalpop_numeric)*100))}%")


mypopup <- glue::glue("<strong>{or_counties_withgeo$NAM}</strong><br />
                      High School Graduation: {or_counties_withgeo$hsgrad}<br />
                      Median Income: {or_counties_withgeo$medincome}") %>% 
  lapply(htmltools::HTML)
```

Final map \^\_\^

```{r}
mapview(or_counties_withgeo, zcol = "medincome", 
         col.regions = RColorBrewer::brewer.pal(9, "Greens"), 
         alpha.regions = 1,
         label = labels,
        popup = mypopup)



```

**Answer:** Clackamas and Marion County both have fairly above average median incomes (\>\$100K), but very average high school graduation rates (87%). For reference Jefferson county has a median income of approximately \$8K, but has a high school graduation rate of 85%

Thanks for reading!
